---
title: "Abraham_Assignment_02"
author: "Reuben Abraham"
date: "2023-02-21"
output: github_document
---
```{r read_csv_tibble}
library(readr)
tibble1 <- read.csv(paste0(getwd(), "/../Input/Project02_SuperStoreOrders.csv"))

```

```{r summary_statistic}
# Create a summary statistic and provide your analysis/observations. 
summary(tibble1)
#' It appears that the average quantity of items ordered is 3.477. The average 
#' discount is 14.29%, which seems to indicate that high discounts are not
#' very common for SuperStore. Additionally, the average profit of SuperStore is
#' $28.64, which is not very high. This seems to indicate that Superstore
#' relies more on selling large quantities of items rather than high value items

```

```{r bar_graph}
# Analyze how the orders are made over the years and by segments. Plot the 
# below graph. Make sure the name of “X-axis” should match. Colors could vary. 
library(ggplot2)
ggplot(tibble1) + 
  geom_bar(aes(x = year, fill=segment), ) 


```

```{r best_seller_bar_graph}
#Which segment is the best seller in the entire dataset? How do you compare the 
#segments? Provide a plot to confirm your claim about the best seller.  
library(ggplot2)
#sales_by_segment_count <- aggregate(segment~sales+as.factor(sales), 
#                                                data = tibble1, length)
#names(sales_by_segment_count) <- c("segment","sales", "ct")

#ggplot(sales_by_segment_count) + 
#  geom_bar(aes(x = segment, y=ct), ) 


library(dplyr)


grp_tbl <- tibble1 %>% group_by(segment)
grp_tbl$sales <- gsub(",", "", grp_tbl$sales )
grp_tbl$numeric_sales <- as.numeric(grp_tbl$sales)

#agg_tbl <- grp_tbl %>% summarise(sum(numeric_sales))


ggplot(grp_tbl) +
  geom_bar(aes (x= segment, y= sum(numeric_sales) ), stat = "identity")
 
#consumer sales appear to be the biggest customer segment.


```


```{r regional_sideways_bar_chart}

ggplot(copy_tibble1) +
  geom_bar(aes(x = reorder(factor(region), region, length), fill=region)) +
  coord_flip() 

# it appears that Central is the region with the most orders, and 
# Canada is the region with the least amount of orders.
  

```


```{r profit graphs by region}
#Use the below code snippet and complete the rest to create the profits graph by region.
#Hint: You are creating a bar plot in a polar coordinate system. 

library(dplyr)

tibble1 %>% 
  mutate(total_profit = sum(profit)) %>%
  group_by(region) %>%
  summarize(total_profit = sum(profit)) %>%
  ggplot() + geom_bar(aes(y = total_profit, x = region) , stat = "identity", 
                      ) + coord_polar()
 


```

```{r total profit }
#Include a density plot to infer the total profit made. Include the orders that
#have profits within the range of [-125, 125].

ggplot(tibble1) + 
  geom_density(aes(x=profit)) +
    scale_x_continuous(limits = c(-125, 125))
#It appears that most of the time, the company is making a low amount of 
#profit for their sold items. 


```


Honors Pledge:
As a student of the Dr. Robert B. Pamplin Jr. School of Business Administration I have read 
and strive to uphold the University’s Code of Academic Integrity and promote ethical behavior. In doing so, I pledge on my honor that I have not given, received, or used any unauthorized materials or assistance on this examination or assignment.  I further pledge that I have not engaged in cheating, forgery, or plagiarism and I have cited all appropriate sources. 

Student Signature:  ______Reuben Abraham__________


